---
title: "R Notebook"
output: html_notebook
---

```{r}
lapply(pre2016list, function1)
```

This is all well and good. But I found it difficult to remember which zone went where. So I've plotted a reference image to go beside the charts.
#Pre-2016 Reference Images

```{r}
arransubsect <- filter(pcs,substr(label,1,4)=="KA27")

lapply(pre2016list, function2)
```

But thinking about it, I could plot all the years together like this.
#Pre-2016 Individual Zones shown on whole island
```{r}
lapply(pre2016list, function3)
```

#Post-2016
```{r}
lapply(post2016list, function1)
```

```{r}
lapply(post2016list, function2)
```

```{r}
lapply(post2016list, function3)
```

#Plot the percentiles as bar charts.
```{r}
arransimd %>%
ggplot(aes(x=year, y=Percentile)) +
  geom_bar(stat="identity") +
  facet_wrap('DataZone') +
  labs(title = "Arran SIMD Datazones", x = "Year", y = "Percentile") +
  theme(plot.title = element_text(hjust = 0.5))
```

#Splitting the bar charts up.
Ideally now I'd like to annotate the above data to highlight the 2016 plots, and show where the change in DZ occurs. (I.e draw a polygon around S01011171-S01011177).
I don't know how to do that yet, so what I'll do now is seperate it into 2 plots.
