---
title: "Front Page Graphics"
output:
  html_document:
    toc: yes
    toc_float: yes
  html_notebook: default
---
These are all the graphics used on the home (https://fergustaylor.github.io/Arran/) page.
N.B The previews shown underneath their code often look cramped here. This is because the image elements shuffle themselves around depending on the available dimensions, rather than scaling at a set ratio. As such you can create much nicer images by running the same code through the console and exporting the image at custom (larger) dimensions. 

#Pre-requisites/Dependencies
```{r}
library(sf)
library(ggplot2) #development version!
## devtools::install_github("tidyverse/ggplot2")
library(tidyverse)
library(readr)
## Not sure about this bit
#library("tidyverse",lib.loc="/Library/Frameworks/R.framework/Versions/3.4/Resources/library")
library(cowplot)
library(sp)
library(gridExtra)
library(dplyr)
library(ggrepel)
library(plyr)
```

```{r}
## Finding the Arran coordinates
arrancoordinates <- read.csv("alldata/ukpostcodes.csv") %>%
 filter(substr(postcode,1,4)=="KA27")

arransubsect <- read_sf("alldata/Scotland_pcs_2011") %>%
filter(substr(label,1,4)=="KA27")
```

```{r}
#Import SIMD data from http://www.gov.scot/Topics/Statistics/SIMD
#https://data.gov.uk/dataset/scottish-index-of-multiple-deprivation-simd-2012
#https://data.gov.uk/dataset/scottish-index-of-multiple-deprivation-simd-2012/resource/d6fa8924-83da-4e80-a560-4ef0477f230b
DZBoundaries2016 <- read_sf("./alldata/SG_SIMD_2016")
DZBoundaries2012 <- read_sf("./alldata/SG_SIMD_2012")
DZBoundaries2009 <- read_sf("./alldata/SG_SIMD_2009")
DZBoundaries2006 <- read_sf("./alldata/SG_SIMD_2006")
DZBoundaries2004 <- read_sf("./alldata/SG_SIMD_2004")
```

```{r}
#Selecting Arran data from Scotland (2016)
#Find postcode look-up from below file for KA27 postcodes. Find unique DZ. Find row positions.
#SIMD2016 <-read.csv("./alldata/00505244.csv")
#Selecting ArranDZ2016
arran2016 <- DZBoundaries2016[c(4672,4666,4669,4671,4667,4668,4670),]
#Reorder arran 2016
reorderedvector<- c("S01011174", "S01011171", "S01011177", "S01011176", "S01011175", "S01011173", "S01011172" )
arran2016 <- arran2016 %>%
  slice(match(reorderedvector, DataZone))

#Find postcode look-up, KA27 postcodes. Find unique DZ. Find row positions.
#Selecting ArranDZ2012
Arrandz2012 <- c(4409,4372,4353,4352,4351,4350,4349)

#2012
arran2012 <- DZBoundaries2012[Arrandz2012,]
#2009
arran2009 <- DZBoundaries2009[Arrandz2012,]
#2006
arran2006 <- DZBoundaries2006[Arrandz2012,]
#2004
arran2004 <- DZBoundaries2004[Arrandz2012,]
```

```{r}
arran20162 <- arran2016 %>%
  select(DataZone, geometry, Percentile)  %>%
  mutate(year="2016")

arran20122 <- arran2012 %>%
  select(DataZone, geometry, Percentile) %>%
  mutate(year="2012")

arran20092 <- arran2009 %>%
  select(DataZone, geometry, Percentile) %>%
  mutate(year="2009")

arran20062 <- arran2006 %>%
  select(DataZone, geometry, Percentile) %>%
  mutate(year="2006")

arran20042 <- arran2004 %>%
  select(DataZone, geometry, Percentile) %>%
  mutate(year="2004")

#Now I add it together
arransimd <- rbind(arran20162,arran20122,arran20092,arran20062,arran20042) %>%
mutate(
    lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
    lat = map_dbl(geometry, ~st_centroid(.x)[[2]])
    )
```

```{r}
simple.sf <- st_as_sf(arrancoordinates, coords=c('longitude','latitude'))
st_crs(simple.sf) <- 4326

exampleshapes <- sf:::as_Spatial(arran2016$geometry)
examplepoints <- sf:::as_Spatial(simple.sf$geom)

examplepoints <- spTransform(examplepoints, CRS("+proj=longlat +datum=WGS84"))
exampleshapes <- spTransform(exampleshapes, CRS("+proj=longlat +datum=WGS84"))

namingdzpostcode <- over(exampleshapes, examplepoints, returnList = TRUE)
```

```{r}
datazones <- unique(arransimd$DataZone)
```

```{r}
function0.5 <- function(argument) 
{
  filter(arransimd, DataZone==argument)
}
```

///

#Front-Page Graphics
```{r}
plot1 <- ggplot() +
  theme_grey() +
  geom_point(data = arrancoordinates, 
             mapping = aes(x = longitude, y = latitude), size=1) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))

plot2 <- ggplot() +
  geom_sf(data = arransubsect) +
  theme_grey() +
  geom_point(data = arrancoordinates, 
             mapping = aes(x = longitude, y = latitude), size=1) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))

plot3 <- ggplot() +
  geom_sf(data = arran2016) +
  theme_grey() +
  geom_point(data = arrancoordinates, 
             mapping = aes(x = longitude, y = latitude), size=1) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))

plot4 <- ggplot() +
  geom_sf(data = arransubsect) +
  geom_sf(data= function0.5("S01004372")) +
  geom_point(data = arrancoordinates[namingdzpostcode[[2]],], 
             mapping = aes(x = longitude, y = latitude), size=1) +
  theme_grey() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))

plot5 <- function0.5("S01004372") %>%
  ggplot() +
  geom_sf() +
  theme_grey() +
  geom_point(data = arrancoordinates[namingdzpostcode[[2]],], 
             mapping = aes(x = longitude, y = latitude), size=1) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))

grid.arrange(plot1, plot2, plot3, plot4, plot5, nrow = 1)
```

```{r}
plot6 <- arran2016 %>%
  ggplot() +
  geom_sf() +
  theme_grey() +
  theme(legend.position="none") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

```{r}
plot7 <- arran2016 %>%
  ggplot() +
  geom_sf(aes(fill = DataZone)) +
  theme_grey() +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

```{r}
plot8 <- arran2016 %>%
mutate(
    lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
    lat = map_dbl(geometry, ~st_centroid(.x)[[2]])
    ) %>%
  ggplot() +
  geom_sf(aes(fill = Percentile)) +
  theme_grey() +
  geom_text(aes(label = Percentile, x = lon, y = lat), size = 2, colour = "white") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

```{r}
grid.arrange(plot6, plot7, plot8, nrow = 1)
```

```{r}
arransimd %>%
ggplot() +
  geom_sf(aes(fill = Percentile)) +
  facet_wrap('year', nrow = 1) +
  theme_grey() +
  geom_text(aes(label = Percentile, x = lon, y = lat), size = 2, colour = "white") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  theme(legend.position="right")  
```
```{r}
function1.5.5 <- function(argument) 
{
  argument %>%
mutate(
    lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
    lat = map_dbl(geometry, ~st_centroid(.x)[[2]])
    ) %>%
  ggplot() +
  geom_sf(aes(fill = Percentile)) +
  facet_wrap('year') +
  theme_grey() +
  geom_text(aes(label = Percentile, x = lon, y = lat), size = 2, colour = "white") +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  theme(legend.position="bottom")  
}

function2.5.1 <- function(argument) 
{
  arransubsect %>%
  ggplot() +
  geom_sf() +
  theme_grey() +
  theme(axis.text.x=element_text(angle=45, hjust = 1)) +
  theme(legend.position="bottom") +
  geom_sf(data= argument, aes(fill = DataZone))
}

function5 <- function(argument, argument2) 
{
  argument %>%
  ggplot() +
  geom_sf() +
  theme_grey() +
  geom_point(data=function6(argument2), mapping = aes(x = longitude, y = latitude), size=1) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))
}

function6 <- function(argument) 
{
  arrancoordinates[namingdzpostcode[[argument]],]
}

function7.5.1 <- function(argument, argument2) 
{
  a <- function1.5.5(argument)
  b <- function2.5.1(argument) 
  c <- function5(argument, argument2)
  grid.arrange(a, b, c, nrow = 1)
}
```

```{r}
function7.5.1(function0.5("S01004372"),2)
```

[See the rest of these plots.](plots.html)
